\documentclass{llncs}
\usepackage{booktabs,chngpage,multirow,tabularx,algorithm,algorithmic,amsmath,xcolor,abstract,graphicx}

\begin{document}
\title{Efficient Grouping Mechanism in Boolean Game to Solving Unweighted MaxSAT Problem}
\maketitle
\begin{abstract}

\end{abstract}
\section{Introduction}
\par par1 MaxSAT problem definition and its applications.
\par par2 Cooperative boolean game and the importance of grouping in boolean game.
\par par3 Introduce the main contributions of our work. (boolean game approach to solving MacSAT problem, map boolean game to undirected graph, efficient grouping mechanism)
\par par4 Organization of this paper.
\section{Related Works}
\par par1 Existing algorithms for MaxSAT problem, these algorithms advantages and disadvantages.
\par par2 Complete algorithms.(branch and bound solving schema, SAT based algoritms)
\par par3 Incomplete algorithms.(CCLS,IRoTS)
\section{XXX Algorithm for MaxSAT Problem}
\subsection{Grouping Mechanism}
\par par1 Players and its payoffs setting in boolean game to solve a MaxSAT instance.
\par par2 The detail of the grouping mechanism.
\subsection{The Framwork of The XXX Algorithm}
\par par1 The detail of the algorithm. 
\section{Experimental Evaluation}
\subsection{The Benchmarks and Experiment Setting}
\par par1 Benchmarks of unweighted MaxSAT problem in MaxSAT 2016 Evaluation.(random, crafted and industrial)
\par par2 Experiments environment, PC's configuration and the settings of experiment parameters.
\subsection{XXX and borealis on random benchmark}
table
\par par1 results analysis and conclusion
\subsection{XXX and CCLS on crafted benchmark}
table
\par par1 results analysis and conclusion
\subsection{XXX and CnC-LS on industrial benchmark}
table
\par par1 results analysis and conclusion

\section{Conclusion and Future Work}
\par par1 Conclusion of our work in this paper. (grouping mechanism, cooperations in game, ).
\par par2 The weakness of our approach, the future work.
\bibliography{myreference}
\bibliographystyle{ieeetr}
\end{document}
